\documentclass[aspectratio=169, t]{beamer}
\usepackage[sidebarleft]{beamerThemeTruman/beamerthemeTruman}
\usepackage{beamerThemeTruman/beamercolorthemeTruman}

\title{Override Request System}
\subtitle{Truman State Math, Statistics, and Computer Science Departments}
\author[Group 1]{Group 1}
\date{November 24, 2020}

\begin{document}
\maketitle

\section{Database and CAS Progress}
\begin{frame}
  \frametitle{Database and CAS Progress}

  

\end{frame}

\section{Logic Progress}
\begin{frame}
  \frametitle{Logic Progress}

\begin{itemize}
    \item Took charge in the process that takes the request from the front-end and returns appropriate response from the system's database.
    \item Necessary to make sure that the communications between front-end and database could be faster and more convenient.
    \item The communication between the two parts was done through the use of API calls.
\end{itemize}

\end{frame}

\begin{frame}
    \frametitle{Logic Progress --- API}

\begin{itemize}
    \item Front-end requests certain data with required parameters (i.e. information) to the API.
    \item The API checks if the given request is valid.
    \begin{itemize}
        \item Returns error message if not.
    \end{itemize}
    \item The API gets the required data from database.
    \item Then returns the data back to the front-end.
\end{itemize}

\end{frame}

\section{Front-End Progress}
\begin{frame}
  \frametitle{Front-End Progress}
  \item Created 5 pages:
  \begin{itemize}
          \begin{Itemize} 
          \item Profile Pages - To fill out user information
            \begin{itemize}
                \item Admin
                \item Student
            \end{itemize}
            \item Admin Page - Contains all requests by all students
            \item Student Page - Contains all requests the student has made
            \item Override Request From - with profile application and input validation!
          \end{Itemize}
  \end{itemize}
  \item We developed these along side a mock API to imitate the connection we would eventually use with the API the logic team has developed.
\end{frame}

\section{Demo}
\sectiontitle{Demo}

\section{}
\maketitle

\end{document}